---
title: "Regression of Sample Survey"
author: "Ali Ahmadi"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
# Set global chunk options
knitr::opts_chunk$set(echo = TRUE)
```

# Data Loading
```{r}
# Load the survey data from the specified file path
data <- read.csv("D:\\R4ds/Advanced_Data_Analysis_R/Data/survey.csv")
```

# Check Data
```{r}
# Display column names, structure, and summary statistics of the dataset
names(data)  # List column names
str(data)    # Display structure of the dataset
summary(data) # Summary statistics for each column
```

# Data Cleaning
```{r}
# Check for missing values
sum(is.na(data)) # Count the number of NA values in the dataset

# Convert 'weekend' column to a factor (categorical variable)
data$weekend <- as.factor(data$weekend)
levels(data$weekend) # Display levels of the 'weekend' factor
```

# Data Inspection
```{r}
# Visualize the distribution of numeric variables using histograms
par(mfrow = c(2, 3)) # Set up a 2x3 grid for plots
for (i in 4:9) {
  hist(data[, i], ylab = "Counts", xlab = names(data)[i], 
       main = paste0("Histogram of ", names(data)[i]))
}
```

# Data Correlations
```{r}
# Compute and display the correlation matrix for selected numeric columns
cor_table <- round(cor(data[, c(4:9)]), 2)
cor_table
```
*Explanation*: The correlation matrix shows the strength of linear relationships between numeric variables. Values close to 1 or -1 indicate strong correlations.

# Categorical Data
```{r}
# Display frequency tables for categorical variables
table(data$weekend)   # Frequency of 'weekend' levels
table(data$num.child) # Frequency of 'num.child' levels
```

# Simple Regression
```{r}
# Fit a simple linear regression model with 'wait' as the predictor for 'overall'
m1 <- lm(overall ~ wait, data = data)
summary(m1)$r.squared # R-squared value (proportion of variance explained)
summary(m1)           # Full summary of the regression model
```
*Explanation*: This model examines the relationship between overall satisfaction (`overall`) and wait time (`wait`). The R-squared value indicates how much of the variation in `overall` is explained by `wait`.

# F-Test and T-Test
```{r}
# Visualize residuals to check normality assumption
hist(m1$residuals, probability = TRUE)
lines(density(m1$residuals), col = "red") # Overlay density curve
```
*Explanation*: The histogram and density plot help assess whether the residuals follow a normal distribution.

```{r}
# Q-Q plot to check normality of residuals
qqnorm(m1$residuals)
qqline(m1$residuals, col = "red")
```

# Skewness and Kurtosis
```{r}
# Use the 'moments' library to test normality assumptions
library("moments")
# Jarque-Bera Test for skewness and kurtosis
# good for data > 25
jarque.test(m1$residuals)  # Test for skewness
anscombe.test(m1$residuals) # Test for kurtosis
```
*Explanation*: These tests check whether the residuals meet the normality assumption. A p-value < 0.05 indicates that the normality assumption is violated.

# Multiple Regression
```{r}
# Fit a multiple regression model with additional predictors
m2 <- lm(overall ~ rides + games + wait + clean, data = data)
summary(m2)$r.squared # R-squared value
summary(m2)           # Full summary of the regression model
```
*Explanation*: This model includes multiple predictors to explain `overall` satisfaction. The R-squared value indicates the proportion of variance explained by all predictors combined.

# Multicollinearity Check
```{r}
# Calculate Variance Inflation Factor (VIF) to check for multicollinearity
library(car)
vif(m2)
```
*Explanation*: A VIF > 10 indicates high multicollinearity, which can affect the reliability of regression coefficients.

# Prediction
```{r}
# Predict 'overall' satisfaction using the coefficients of m2
m2$coefficients %*% c(1, 2, 3, 1, 9) # Example prediction
```

# Standardized Regression
```{r}
# Standardize numeric variables and fit a regression model
df <- as.data.frame(scale(data[, c(4:9)]))
m3 <- lm(overall ~ ., data = df)
summary(m3)$r.squared # R-squared value
summary(m3)           # Full summary of the regression model
```
*Explanation*: Standardizing variables ensures that all predictors are on the same scale, which is useful for comparing coefficients.

# Adding Categorical Data
```{r}
# Include categorical variables in the regression model
data$weekend <- as.factor(data$weekend)
data$num.child <- as.factor(data$num.child)
m4 <- lm(overall ~ ., data = data)
summary(m4)
```

# Interaction Effects
```{r}
# Fit a model with interaction terms
m7 <- lm(overall ~ distance + rides + games + wait + clean +
           weekend + num.child +
           rides:num.child + games:num.child + wait:num.child +
           clean:num.child + rides:weekend + games:weekend +
           wait:weekend + clean:weekend, data = data)
summary(m7)
vif(m7) # Check for multicollinearity
```
*Explanation*: Interaction terms allow us to examine how the effect of one variable depends on the level of another variable.

# Final Model
```{r}
# Fit the final regression model
m8 <- lm(overall ~ rides + games + wait + clean + 
           num.child + wait:num.child, data = data)
summary(m8)
```
*Explanation*: The final model includes significant predictors and interaction terms to explain `overall` satisfaction.

# Model Diagnostics
```{r}
# Diagnostic plots for the final model
plot(m8)

# Prediction vs Actual
plot(data$overall, fitted(m8), col = "blue",
     xlim = c(0, 10), ylim = c(0, 10),
     xlab = "Actual Overall Satisfaction", ylab = "Fitted Overall Satisfaction")
abline(a = 0, b = 1, col = "red")
```
*Explanation*: Diagnostic plots help assess the model's assumptions, and the prediction vs. actual plot shows how well the model fits the data.

