---
title: "Regression of Sample Survey"
author: "Ali Ahmadi"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
# Set global chunk options
knitr::opts_chunk$set(echo = TRUE)
```

# Data Loading
```{r}
# Load the survey data from the specified file path
data <- read.csv("D:\\R4ds/Advanced_Data_Analysis_R/Data/survey.csv")
```

# Check Data
This dataset includes information from a recreational park, focusing on overall visitor satisfaction. It consists of various variables such as waiting times, visitor distances, the number of children accompanying visitors, and whether the visit occurred on a weekend. In the code block below, we will examine the class of these variables and their corresponding data types.
```{r}
# Display column names, structure, and summary statistics of the dataset
names(data)  # List column names
str(data)    # Display structure of the dataset
summary(data) # Summary statistics for each column
head(data) # show top rows of dataset
```

# Data Cleaning
In this section, we will check for the presence of NA values in the dataset. From the output of summary(data), we can confirm that there are no NA values present. The 'Weekend' variable contains two character values: 'Yes' and 'No'. We can convert this variable into a factor with two levels for better analysis.
```{r}
# Check for missing values
sum(is.na(data)) # Count the number of NA values in the dataset

# Convert 'weekend' column to a factor (categorical variable)
data$weekend <- as.factor(data$weekend)
levels(data$weekend) # Display levels of the 'weekend' factor
```

# Data Inspection
By examining the histogram of the data, we can observe that there are a sufficient number of values to analyze. This allows us to assess the distribution of each numeric variable effectively.
```{r}
# Visualize the distribution of numeric variables using histograms
par(mfrow = c(2, 3)) # Set up a 2x3 grid for plots
for (i in 4:9) {
  hist(data[, i], ylab = "Counts", xlab = names(data)[i], 
       main = paste0("Histogram of ", names(data)[i]))
}
```

# Data Correlations
By applying correlation analysis to the numeric variables, we can identify dependencies between some of them and the overall target variable. Additionally, we can assess whether there are strong correlations among the variables themselves. The correlation matrix illustrates the strength of the linear relationships between numeric variables, with values close to 1 or -1 indicating strong correlations.
```{r}
# Compute and display the correlation matrix for selected numeric columns
cor_table <- round(cor(data[, c(4:9)]), 2)
cor_table
```


# Categorical Data
num.child is not categorical data, however we can consider it as a categorical data and check the number of data in each category by using table function.
```{r}
# Display frequency tables for categorical variables
table(data$weekend)   # Frequency of 'weekend' levels
table(data$num.child) # Frequency of 'num.child' levels
```

# Simple Regression
so up to here, we should follow these steps:
1- check and oveview dataset 
2- apply data cleaning 
3- plot histogram of numerical variables to check the distribution of data
4- check the categorical data
5- start a regression model 

This model examines the relationship between overall satisfaction (`overall`) and wait time (`wait`). The R-squared value indicates how much of the variation in `overall` is explained by `wait`.
```{r}
# Fit a simple linear regression model with 'wait' as the predictor for 'overall'
m1 <- lm(overall ~ wait, data = data)
summary(m1)$r.squared # R-squared value (proportion of variance explained)
summary(m1)           # Full summary of the regression model
```

# F-Test and T-Test

by using F-test and T-test we can be somehow sure that there is a relation between variables and target. The histogram and density plot help assess whether the residuals follow a normal distribution.

```{r}
# Visualize residuals to check normality assumption
hist(m1$residuals, probability = TRUE)
lines(density(m1$residuals), col = "red") # Overlay density curve
```

```{r}
# Q-Q plot to check normality of residuals
qqnorm(m1$residuals)
qqline(m1$residuals, col = "red")
```

# Skewness and Kurtosis
These tests check whether the residuals meet the normality assumption. A p-value < 0.05 indicates that the normality assumption is violated.
```{r}
# Use the 'moments' library to test normality assumptions
library("moments")
# Jarque-Bera Test for skewness and kurtosis
# good for data > 25
jarque.test(m1$residuals)  # Test for skewness
anscombe.test(m1$residuals) # Test for kurtosis
```
After performing the regression analysis, we can evaluate the normality of the residuals using the following methods:
1- A histogram of the residuals to assess their distribution.
2- A QQ plot of the residuals to examine how well they align with a normal distribution.
3- Evaluation of skewness and kurtosis, checking for values greater than 25, to determine if we can reject the normality assumption of the residuals.

# Multiple Regression
This model includes multiple predictors to explain `overall` satisfaction. The R-squared value indicates the proportion of variance explained by all predictors combined.
```{r}
# Fit a multiple regression model with additional predictors
m2 <- lm(overall ~ rides + games + wait + clean, data = data)
summary(m2)$r.squared # R-squared value
summary(m2)           # Full summary of the regression model
```

# Multicollinearity Check
```{r}
# Calculate Variance Inflation Factor (VIF) to check for multicollinearity
library(car)
vif(m2)
```
*Explanation*: A VIF > 10 indicates high multicollinearity, which can affect the reliability of regression coefficients.

# Prediction
```{r}
# Predict 'overall' satisfaction using the coefficients of m2
m2$coefficients %*% c(1, 2, 3, 1, 9) # Example prediction
```

# Standardized Regression
In the dataset, the values of distance are in a different range compared to the other features. To enhance our model's performance, we standardized the dataset values using the scale function.Standardizing variables ensures that all predictors are on the same scale, which is useful for comparing coefficients.


```{r}
# Standardize numeric variables and fit a regression model
df <- as.data.frame(scale(data[, c(4:9)]))
m3 <- lm(overall ~ ., data = df)
summary(m3)$r.squared # R-squared value
summary(m3)           # Full summary of the regression model
```

# Adding Categorical Data to the Model
```{r}
# Include categorical variables in the regression model
data$weekend <- as.factor(data$weekend)
data$num.child <- as.factor(data$num.child)
m4 <- lm(overall ~ ., data = data)
summary(m4)
```

# Interaction Effects
Examine the inteaction of two variables based on correlation table. Interaction terms allow us to examine how the effect of one variable depends on the level of another variable.
```{r}
# Fit a model with interaction terms
m7 <- lm(overall ~ distance + rides + games + wait + clean +
           weekend + num.child +
           rides:num.child + games:num.child + wait:num.child +
           clean:num.child + rides:weekend + games:weekend +
           wait:weekend + clean:weekend, data = data)
summary(m7)
vif(m7) # Check for multicollinearity
```


# Final Model
```{r}
# Fit the final regression model
m8 <- lm(overall ~ rides + games + wait + clean + 
           num.child + wait:num.child, data = data)
summary(m8)
```
*Explanation*: The final model includes significant predictors and interaction terms to explain `overall` satisfaction.

# Model Diagnostics
```{r}
# Diagnostic plots for the final model
plot(m8)

# Prediction vs Actual
plot(data$overall, fitted(m8), col = "blue",
     xlim = c(0, 10), ylim = c(0, 10),
     xlab = "Actual Overall Satisfaction", ylab = "Fitted Overall Satisfaction")
abline(a = 0, b = 1, col = "red")
```
*Explanation*: Diagnostic plots help assess the model's assumptions, and the prediction vs. actual plot shows how well the model fits the data.

